How to improve PCA based methods of genome scan using ecological data: detecting selection using RDA.

### 2017-04-19 article_genome_scan.tex
update

\begin{figure}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/R2.eps}
\end{center}
\caption{Percentage of variance explained by the first three ordination axis when the RDA is performed on all SNPs (red color) and when it is performed on the set of outliers loci (blue color). Values are averaged across the 100 simulated datasets.}%
\label{fig:R2}%
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/varexplainedPopulus.eps}
\end{center}
\caption{Percentage of variance explained by the first three ordination axis when the RDA is performed on all SNPs (red color) and when it is performed on the set of outliers loci (175 loci - blue color).}%
\label{fig:varexplainedPopulus}%
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/R2.eps}
\end{center}
\caption{Proportion of variance explained by the first three ordination axis when the RDA is performed on all SNPs (red color) and when it is performed on the set of outliers loci (blue color). Values are averaged across the 100 simulated datasets.}%
\label{fig:R2}%
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[height=0.4\textheight]{figures/varexplainedPopulus.eps}
\end{center}
\caption{Proportion of variance explained by the first three ordination axis when the RDA is performed on all SNPs (red color) and when it is performed on the set of outliers loci (175 loci - blue color).}%
\label{fig:varexplainedPopulus}%
\end{figure}
